### 2023-08-21 manuscript.tex
Merge pull request #17 from habi/rootstock-2023-08-21 [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5926946849

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.1...37cc38a386f502ad80dd15509062ce55dc9330d8\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/37cc38a386f502ad80dd15509062ce55dc9330d8/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/37cc38a386f502ad80dd15509062ce55dc9330d8}{habi/EAWAG-manuscript@37cc38a}
on August 15, 2023.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187} ·
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://mastodon.social/@habi}{@habi@mastodon.social}
  Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
\item
  \textbf{Mikki Law}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/mlaw-migalig}{mlaw-migalig}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Kassandra Ford}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633} ·
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/kassthefish}{kassthefish}
  Department of Biological Sciences, George Washington University, USA; Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Marcel Häsler}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/mphaesler}{mphaesler}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Ole Seehausen}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434} ·
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/OleSeehausen}{OleSeehausen}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Ruslan Hlushchuk}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996} ·
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/RuslanHlushchuk}{RuslanHlushchuk}
  Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 15 Aug 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 15 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 15 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/28f3d2d2eba7b007cc01d09b5cd6d4e926848aa5}{habi/EAWAG-manuscript@28f3d2d}
on August 21, 2023.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://mastodon.social/@habi}{@habi@mastodon.social}
  Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
\item
  \textbf{Mikki Law}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/mlaw-migalig}{mlaw-migalig}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Kassandra Ford}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-4413-2633}{0000-0002-4413-2633}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/kassthefish}{kassthefish}
  Department of Biological Sciences, George Washington University, USA; Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Marcel Häsler}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/mphaesler}{mphaesler}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Ole Seehausen}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-6598-1434}{0000-0001-6598-1434}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/OleSeehausen}{OleSeehausen}
  Aquatic Ecology and Evolution, Institute of Ecology and Evolution, University of Bern, CH-3012 Bern, Switzerland; Department of Fish Ecology and Evolution, Eawag, Swiss Federal Institute for Aquatic Science and Technology, CH-6047 Kastanienbaum, Switzerland
\item
  \textbf{Ruslan Hlushchuk}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-6722-8996}{0000-0002-6722-8996}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/RuslanHlushchuk}{RuslanHlushchuk}
  Institute of Anatomy, University of Bern, Baltzerstrasse 2, CH-3012 Bern, Switzerland
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 21 Aug 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 21 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 21 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
